---
title: "Causal Inference"
output: html_notebook
---

In case packages are not installed:
```{r}
install.packages("devtools")
devtools::install_github("gpapadog/DAPSm")
```



```{r}
data <- toyData2
toyData2$prop.scores <- glm(Z ~ X1 + X2 + X3 + X4, family = binomial,
                            data = toyData2)$fitted.values
daps <- DAPSest(toyData2, out.col = 2, trt.col = 1, caliper = 0.3,
                weight = 0.7, coords.columns = c(4, 5),
                pairsRet = TRUE, cov.cols = 6:9, cutoff = 0.1,
                coord_dist = TRUE, caliper_type = 'DAPS',
                matching_algorithm = 'greedy')
bal <- CalcDAPSWeightBalance(toyData2, weights = seq(0, 1, length.out = 40),
                             cov.cols = 6:9, trt.col = 1,
                             coords.columns = c(4, 5), caliper = 0.3,
                             matching_algorithm = 'greedy')
PlotWeightBalance(bal$balance, weights = seq(0, 1, length.out = 40), cutoff = 0.15)


```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
